\begin{thebibliography}{99} 

\bibitem{App}
Y. Ezra, U. Mahlab, M. Haridim, and B.I. Lembrikov, ``Applications of All-Optical Signal Processing in Modern Optical Communications, '' {\it ICTON}, no.Tu.B4.4, pp.328--331, Rome, The Italy, Jul. 2007.

\bibitem{ultrafast_qdsoa}
H. Taleb, and K. Abedi, ``Ultrafast All-Optical Signal Processing Using Optically Pumped QDSOA-Based Mach-Zehnder Interferometers, '' {\it IEEE J. Sel. Top. Quantum Electron}, vol.19, no.5, Oct. 2013.

\bibitem{current_cpu}
(2017, Dec. 8). {\it Intel Core i7-5557U specifications} [Online]. Available: http://www.cpu-world.com/CPUs/Core\_i7/Intel-Core\%20i7-5557U\%20Mobile\%20processor.html

\bibitem{non_linear}
山下真司 著 『光ファイバ通信のしくみがわかる本』 (技術評論社， 2002)

\bibitem{devices}
黒川隆志 著 『光機能デバイス』 (共立出版， 2004)

\bibitem{optic}
前田譲治，海老澤賢史 著 『光工学が一番わかる(しくみ図解)』 (技術評論社， 2011)

% refs of QD
\bibitem{qd_soa}
T. Akiyama, M. Sugawara, and Y. Arakawa, ``Quantum-Dot Semiconductor Optical Amplifiers, '' {\it Proc. of the IEEE}, vol.95, no.9, pp.1757--1766, Sep. 2007.

\bibitem{four_energies1}
S. Izadyar, M. Razaghi, and A. Hassanzadeh, ``Quantum dot semiconductor optical amplifier: role of second excited state on ultrahigh bit-rate signal processing, '' {\it Appl. Opt}, vol.56, no.12, pp.3599--3607, Apr. 2017.

\bibitem{four_energies2}
M. Sugawara, N. Hatori, H. Ebe, M. Ishida, Y. Arakawa, T. Akiyama, K. Otsubo, and Y. Nakata, ``Modeling room-temperature lasing spectra of 1.3-${\rm \mu}$m self-assembled InAs/GaAs quantum-dot lasers: Homogeneous broadening of optical gain under current injection, '' {\it J. Appl. Phys}, vol. 97, 2005.

\bibitem{theory_of_qdsoa}
M. Sugawara, H. Ebe, N. Hatori, M. Ishida, Y. Arakawa, T. Akiyama, K. Otsubo, and Y. Nakata, ``Theory of optical signal amplification and processing by quantum-dot semiconductor optical amplifiers, '' {\it Phys. Rev. B}, vol. 69, 2004.

\bibitem{qd_book}
舛本泰明 著 『量子ドットの基礎と応用』 (裳華房， 2015)

\bibitem{qdsoa_1300nm}
T. Vallaitis, C. Koos, R. Bonk, W. Freude, M. Laemmlin, C. Meuer, D. Bimberg, and J. Leuthold, ``Slow and fast dynamics of gain and phase in a quantum dot semiconductor optical amplifier, '' {\it Opt. Express}, vol.16, no.1, pp.170--178, Jan. 2004.

\bibitem{qdsoa_1550nm}
Aaron J. Zilkie, J. Meier, P. Smith, M. Mojahedi, J. Aitchison, P. Poole, C. Allen, P. Barrios, and D. Poitras, ``Femtosecond gain and index dynamics in an InAs/InGaAsP quantum dot amplifier operating at 1.55${\rm \mu}$m, '' {\it Opt. Express}, vol.14, no.23, pp.11453--11459, Nov. 2006.

\bibitem{qd_dispersion}
J. Kim, M. Laemmlin, C. Meuer, D. Bimberg, and G. Eisenstein, ``Theoretical and Experimental Study of High-Speed Small-Signal Cross-Gain Modulation of Quantum-Dot Semiconductor Optical Amplifiers, '' {\it IEEE J. Quantum Electron}, vol.45, no.3, pp.240--248, Feb. 2009.

\bibitem{on_the_noise_properties}
A. Bilenca, and G. Eisenstein, ``On the Noise Properties of Linear and Nonlinear Quantum-Dot Semiconductor Optical Amplifiers: The Impact of Inhomogeneously Broadened Gain and Fast Carrier Dynamics, '' {\it IEEE J. Quantum Electron}, vol.40, no.6, pp.690--702, Jun. 2004.

\bibitem{qd_low_noise}
T. Berg, and J. Mork, ``Quantum dot amplifiers with high output power and low noise, '' {\it Appl. Phys. Lett}, vol.82, no.18, pp.3083--3085, May. 2003.

\bibitem{qd_soa_rate_equation} 
K. Abedi, and H. Taleb, ``Phase Recovery Acceleration in Quantum-Dot Semiconductor Optical Amplifiers, " {\it J. Lightwave Technol}, vol.30, no.12, pp.1924--1930, Jun. 2012.

\bibitem{bf_and_fca_phase}
J. Kim, C. Meuer, D. Bimberg, and G. Eisenstein, ``Effect of Inhomogeneous Broadening on Gain and Phase Recovery of Quantum-Dot Semiconductor Optical Amplifiers, '' {\it IEEE J. Quantum Electron}, vol.46, no.11, pp.1670--1680, Nov. 2010.

\bibitem{NSSM1}
H. Taleb, K. Abedi, and S. Golmohammadi, ``Quantum-Dot Semiconductor Optical Amplifiers: State Space Model versus Rate Equation Model, " {\it Adv Optoelectron}, no. 831852, Feb. 2013.

\bibitem{NSSM2}
H. Taleb, K. Abedi, and S. Golmohammadi, ``A simple and accurate dynamical modeling of quantum-dot semiconductor optical amplifiers, " {\it Int J Numer Model El}, devices and fields, no. 27, pp.79--88, May. 2013.

% refs of PC
\bibitem{loss_coefficient}
X. Li, T. Wang, C. Dong, J. Tang, B. Liu, and Y. He, ``Modified Drude model for free-carrier absorption due to bound-to-continuum transition in quantum-dot semiconductor optical amplifier, '' {\it J. Appl. Phys}, vol.114, issue 15, Oct. 2013.

\bibitem{photonic_crystal1}
J. Li, T. White, L. Faolain, A. Iglesias, and T. Krauss, ``Systematic design of flat band slow light in photonic crystal waveguides, " {\it Opt. Express}, vol.16, no.9, pp.6227--6232, Apr. 2008.

\bibitem{photonic_crystal2}
J. Lourtioz, H. Benisty, V. Berger, J. Gerard, D. Maystre, A. Tchelnokov, and D. Pagnoux 著, 木村達也 訳 『フォトニック結晶―ナノ光デバイスを目指して―』 (オーム社， 2012)

\bibitem{slow_light1}
T. Krauss, ``Slow light in photonic crystal waveguides, " {\it J Phys D Appl Phys}, vol.40, pp.2666--2670, Apr. 2007.

\bibitem{slow_light2}
T. Baba, ``Slow light in photonic crystals, " {\it Nat Photonics}, vol.2, pp.465--473, Aug. 2008.

\bibitem{effective_index_approximations}
M. Hammer, and O. Ivanova, ``Effective index approximations of photonic crystal slabs: a 2-to-1-D assessment, " {\it Opt Quant Electron}, vol.41, pp.267--283, Mar. 2009.

\bibitem{model_of_pc_qdsoa}
H. Taleb, and K. Abedi, ``Modeling and Design of Photonic Crystal Quantum-Dot Semiconductor Optical Amplifiers, " {\it IEEE Trans. Electron Devices}, vol.61, no.7, pp.2419--2426, May. 2014.

\bibitem{pc_qd_soa_rate_equation} 
K. Abedi, and H. Taleb, ``Optical Gain， Phase， and Refractive Index Dynamics in Photonic Crystal Quantum-Dot Semiconductor Optical Amplifiers, " {\it IEEE J. Quantum Electron}, vol.50, no.8, pp.605--612, Jun. 2014.

\bibitem{GaAsIndex}
J. Kim, and A. Sarangan, ``Temperature-dependent Sellmeier equation for the refractive index of ${\rm Al_{x}Ga_{1-x}As}$, " {\it Opt. Lett}, vol.32, no.5, pp.536--538, Mar. 2007.

\bibitem{InGaAsIndex}
(2018, Feb. 5). ``Refractive Index n of ${\rm In_{x}Ga_{1-x}As}$ Alloys, " [Online]. Available: http://www.batop.com/information/n\_InGaAs.html.

\bibitem{Ultrafast}
Y. Ezra, B. Lembrikov, and M. Haridim, ``Ultrafast All-Optical  Processor Based on Quantum-Dot Semiconductor Optical Amplifiers, '' {\it IEEE J. Quantum Electron}, vol.45, no.1, pp.34--41, Jan. 2009.

\bibitem{Rostami}
A. Rostami, H. Nejad, R. Qartavol, and H. Saghai, ``Tb/s Optical Logic Gates Based on Quantum-Dot Semiconductor Optical Amplifiers, '' {\it IEEE J. Quantum Electron}, vol.46, no.3, pp.354--360, Mar. 2010.

\bibitem{nano_photonic}
(2018, Feb. 5). ``Nanophotonics and integrated optics Photonic Crystal Cavities, " {\it CST AG Whitepaper} [Online]. Available: https://www.cst.com/Content/Media/External/CST-Whitepaper-Photonic-EPraxis.pdf

\bibitem{80Gbps}
H. Dong, H. Sun, Q. Wang, N. Dutta, and J. Jaques, ``80 Gb/s All-optical logic AND operation using Mach-Zehnder interferometer with differential scheme, '' {\it Opt Commun}, vol.265, no.1, pp.79--83, Sep. 2006.

\bibitem{Gayen}
D. Gayen, A. Bhattachryya, T. Chattopadhyay, and J. Roy, ``Ultrafast All-Optical Half Adder Using Quantum-Dot Semiconductor Optical Amplifier-Based Mach-Zehnder Interferometer, " {\it J. Lightwave Technol}, vol.30, no.21, pp.3387--3393, Nov. 2012.
	
\end{thebibliography}